---
title: "case_study"
author: "nz2333"
date: "10/29/2021"
output: html_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


##load the dataset
```{r}
data("nyc_airbnb")
```

# How many retals are there, what type, what places?
```{r}
nyc_airbnb = 
  nyc_airbnb %>%
  mutate(stars = review_scores_location / 2) %>%
  rename(borough = neighbourhood_group)
```

count things:
```{r}
nyc_airbnb %>%
  janitor::tabyl(borough, room_type)
```
same thing:
```{r}
nyc_airbnb %>%
  count(borough, room_type) %>%
  pivot_wider(
    names_from = room_type, 
    values_from = n
  )
```

# Is price correlated with the review score?
```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y = price)) +
  geom_point()+
  facet_grid(. ~room_type)
```

# Which neighborhood is most popular ? most expensive?
```{r}
nyc_airbnb %>%
  group_by(neighbourhood) %>%
  summarize(mean_price = mean(price, na.rm = TRUE)) %>%
  arrange(mean_price)

nyc_airbnb %>%
  group_by(neighbourhood) %>%
  summarize(mean_review = mean(stars, na.rm = TRUE)) %>%
  arrange(-mean_review)
```

# Distance to subway and ratings
```{r}
nyc_airbnb %>%
  filter(price < 500) %>%
  sample_n(5000) %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = 0.5)
```
*can tell from the mapping, closer to central mahanttan, price gets higher. 

# Retry leaflet
```{r}
nyc_airbnb %>%
  filter(price < 500) %>%
  sample_n(1000) %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(~lat, ~long)
```
* AddTiles: the background


# Which neighborhood has the highest reviews?
# Is availability related to price?
# Is room type related to neighborhood?
# Is length of stay related to neightborhood group?




